---
title: "Multiclass classificaiton: marketing data"
output: html_notebook
---


# 9 Multiclass classificaiton: marketing data
```{r}
library(gbm)
```


```{r}
occup = read.csv("./data/occup.csv")
```

```{r}
# label the col names
# Refer to occup.txt for the varaibles description

occuplabs<-c("occup", "TypeHome",
             "sex","MarStat", "age", "Edu","Income",
             "LiveBA","DualInc","Persons", "Under18", "HouseStat",
             "Ethnic")
  # Names for predictors and response
colnames(occup) =occuplabs

```

```{r}
# Turn the predictors into qualitative variables.
occup[] = lapply(occup, factor)
  col_names = names(occup)

```


Split data in 0.8 (80% training and 20% test) one for training the other for test

```{r}
library(caTools)
```

```{r}
split = sample.split(occup$occup, SplitRatio = 0.8)
occup.train = subset(occup, split == TRUE)
occup.test = subset(occup, split == FALSE)
```

Fit the data into a gbm
```{r}
gbm = gbm(occup~., data=occup.train,interaction.depth=4,shrinkage=.05, n.trees=5000,bag.fraction=0.5,cv.folds=5, distribution="multinomial",verbose=F)
```


Use Cross validation to determine best iteration

```{r}
# Use cross validaiton to select the best iteration
best.iter=gbm.perf(gbm,method="cv")
```


Refit the model

```{r}
gbm = gbm(occup~., data=occup.train,interaction.depth=4,shrinkage=.05, n.trees=best.iter,bag.fraction=0.5,cv.folds=5, distribution="multinomial",verbose=F)
```


```{r}
gbm.predict = data.frame(predict(gbm, type = "response", occup.test,n.trees = best.iter-10))
colnames(gbm.predict) = c('Professional/Managerial',"SalesWrk","FactoryWrk","ClericalWrk","Homemaker","Student","Military","Retired","Unemployed")
```

```{r}
gbm.predict$Cat = apply(gbm.predict, 1, which.max)
```

```{r}
gbm.predict = gbm.predict$Cat
```


This is our confusion matrix.
```{r}
cm = table(gbm.predict, occup.test$occup)
cm
```

(a)
Misclassfication overall error is

```{r}
(cm[1,1]+cm[2,2]+cm[3,3]+cm[4,4]+cm[5,5]+cm[6,6]+cm[7,7]+cm[8,8]+cm[9,9])/sum(cm)
```


Misclassifcation error for class 1

```{r}
1-cm[1,1]/sum(cm[1,])
```


Misclassifcation error for class 2
```{r}
1-cm[2,2]/sum(cm[2,])
```

Misclassifcation error for class 3
```{r}
1-cm[3,3]/sum(cm[3,])
```


Misclassifcation error for class 4
```{r}
1-cm[4,4]/sum(cm[4,])
```



Misclassifcation error for class 5

```{r}
1-cm[5,5]/sum(cm[5,])
```


Misclassifcation error for class 6
```{r}
1-cm[6,6]/sum(cm[6,])
```


Misclassifcation error for class 7


```{r}
1-cm[7,7]/sum(cm[7,])
```

Misclassifcation error for class 8

```{r}
1-cm[8,8]/sum(cm[8,])
```


Misclassifcation error for class 9

```{r}
1-cm[9,9]/sum(cm[9,])
```


(b)

Most important variables:

Age, educaiton and income are the most important variables. 

```{r}
summary(gbm)
```

